Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
minor edit to frequency response of the wavelet

	&=\frac{1}{2}\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}

@@

Two different experiments were designed to test the framework. In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run. This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization. \dean{the frequency response of the observed field used to decide on the level...} . In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e. $j=0$ to $j=4$. All parameters for the model are given in Table~\ref{tab:Parameters}.

>>>>

	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}

@@

Two different experiments were designed to test the framework. In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run. This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization. \dean{the frequency response of the observed field used to decide on the level...} In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e. $j=0$ to $j=4$. All parameters for the model are given in Table~\ref{tab:Parameters}.
